A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by a pile of money from a funding agency.}

### 2017-02-16 paper/paper.tex
Describe the down and sip stuff

\paragraph{Unlabelled, undirected, connected} This class of instances are shown
in \cref{figure:plain-connected-cumulative} (again, ??kdown does not support the connected problem).  These results are very similar to
the corresponding experiment in \cref{figure:plain-cumulative} in which the
subgraph is not required to be connected.

@@

\paragraph{Large subgraph isomorphism instances} We also ran the algorithms on
a set of 5725 larger instances used in recent studies of subgraph
isomorphism~\citep{DBLP:conf/lion/KotthoffMS16} and maximum common
subgraph~\citep{UpcomingAAAIPaper}.  This benchmark set includes real-world
graphs and graphs generated using random models.  Pattern graphs range from 4
vertices to 900 with a median of 80; target graphs range from 10 vertices to
6671 with a median of 561.  Cumulative runtimes including the kdown algorithm
from~\citep{UpcomingAAAIPaper} which was the previous state of the art for this
benchmark, are in \cref{figure:sip-cumulative}.  This is a challenging set of
instances, and more than half of the instances cannot be solved within a
timeout of 1000 seconds by any of the solvers. Moreover the CP-FC algorithm and
the clique encoding run out of memory on many of the instances.  \McSplit\
is the strongest solver overall for this dataset.

@@

?? Let's put this hereish: I'VE RE-ADDED A SHORTER VERSION OF THIS
PARAGRAPH, WHICH WAS COMMENTED OUT BY PATRICK. IT NEEDS WORK, BUT WE NEED TO
EXPLAIN THE SIP EXPERIMENT. We can modify the \McSplit\ algorithm to use a
top-down strategy based on \citet{UpcomingAAAIPaper} by calling the main
\FuncSty{McSplit} method once per goal size ($g, g-1, g-2, \dots$).  We
backtrack (\lineref{PruneSearch} of \cref{McCliqueAlg}) when the bound is
strictly less than the goal size, and terminate when a solution of the goal
size is found.

>>>>

\paragraph{Unlabelled, undirected, connected} This class of instances are shown
in \cref{figure:plain-connected-cumulative}.  These results are very similar to
the corresponding experiment in \cref{figure:plain-cumulative} in which the
subgraph is not required to be connected.

@@

\paragraph{Large subgraph isomorphism instances} We also ran the algorithms on
a set of 5725 larger instances used in recent studies of subgraph
isomorphism~\citep{DBLP:conf/lion/KotthoffMS16} and maximum common
subgraph~\citep{UpcomingAAAIPaper}.  This benchmark set includes real-world
graphs and graphs generated using random models.  Pattern graphs range from 4
vertices to 900 with a median of 80; target graphs range from 10 vertices to
6671 with a median of 561. Cumulative runtimes on these instances are shown in
\cref{figure:sip-cumulative}.  This is a challenging set of instances, and more
than half of the instances cannot be solved within a timeout of 1000 seconds by
any solver. Furthermore, the CP-FC algorithm and the clique encoding run out of
memory on many of the instances (these are treated as timeouts).

The basic \McSplit\ is beaten by the $k\downarrow$ algorithm of
\citet{UpcomingAAAIPaper} on this dataset. However, we can modify the \McSplit\
algorithm to use a top-down strategy similar to that used by $k\downarrow$  by
calling the main \FuncSty{McSplit} method once per goal size ($g, g-1, g-2,
\dots$); we backtrack (\lineref{PruneSearch} of \cref{McCliqueAlg}) when the
bound is strictly less than the goal size, and terminate when a solution of the
goal size is found. We expect that this could do well because in many cases the
matching covers nearly all of the smaller graph---indeed,
\cref{figure:sip-cumulative} shows that this approach is the strongest on these
instances.

@@
